Geometric Information for Image Understanding

### 2018-06-05 chapters/introduction/introduction.tex
introduce mystyle.sty

Specifically, Use of overhead image (or map layout) is useful.
overhead imagery are useful and easy to access, gowing densely
available in space and time.

@@

  \item \textbf{\chapref{dependence} - Are Deep Image Representations
    Geo-Informative?} \newline \newline In this chapter, we
    investigate the usefulness of deep image representations,
    extracted from convolutional neural networks applied to
    traditional vision tasks, for problems in geospatial image
    analysis. In particular, we analyze their discriminative ability
    with regard to location through several problem settings,
    including region identification in ground-level imagery,
    understanding and interpreting overhead images, and cross-view
    image matching.  Our results demonstrate the effectiveness of deep
    image representations extracted from CNNs, on both ground-level
    and overhead imagery, for capturing geographically discriminative
    features relating image appearance to geographic location.  This
    points to a promising direction for future research in building
    deep-learning based models that are directly targeted at problems
    of localization and location-related feature extraction from
    ground-level and overhead imagery.  This work was originally
    reported in~\cite{workman2015geocnn}. \newline

>>>>

\brief{Specifically, Use of overhead image (or map layout) is useful.
overhead imagery are useful and easy to access, gowing densely
available in space and time.}
The use of overhead imagery has been proved useful for image
understanding.
Several methods have been recently proposed to jointly reason about
co-located aerial and ground image pairs. Luo
\etal~\cite{luo2008event} demonstrate that aerial imagery can aid
in recognizing the visual content of a geo-tagged ground image.
M{\'a}ttyus \etal~\cite{mattyus2016hd} perform joint inference over
monocular aerial imagery and stereo ground images for fine-grained
road segmentation. Wegner \etal~\cite{wegner2016cataloging} build a
map of street trees. Given the horizon line and the camera intrinsics,
Ghouaiel and Lef{\`e}vre~\cite{ghouaiel2016coupling} transform
geo-tagged ground-level panoramas to a top-down view to enable
comparisons with aerial imagery for the task of change detection.
Recent work on cross-view image
geolocalization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
 has shown that convolutional neural
networks are capable of extracting features from aerial imagery
that can be matched to features extracted from ground imagery.
Vo \etal~\cite{vo2016localizing} extend this line of work,
demonstrating improved geolocalization performance by applying an
auxiliary loss function to regress the ground-level camera orientation
with respect to the aerial image. To our knowledge, our work is the
first work to explore predicting the semantic layout of a ground
image from an aerial image.

@@

  \item \textbf{\chapref{dependence} - Are Deep Image Representations
    Geo-Informative?} \newline \newline In this chapter, we
    investigate the usefulness of deep image representations,
    extracted from convolutional neural networks applied to
    traditional vision tasks, for problems in geospatial image
    analysis. In particular, we analyze their discriminative ability
    with regard to location through several problem settings,
    including region identification in ground-level imagery,
    understanding and interpreting overhead images, and cross-view
    image matching.  Our results demonstrate the effectiveness of deep
    image representations extracted from CNNs, on both ground-level
    and overhead imagery, for capturing geographically discriminative
    features relating image appearance to geographic location.  This
    points to a promising direction for future research in building
    deep-learning based models that are directly targeted at problems
    of localization and location-related feature extraction from
    ground-level and overhead imagery. \newline
